Geometric signs reveal changes in social structures and networks during the Western Eurasian Aurignacian

### 2025-08-23 paper/paper.qmd
edit

Our results do not suggest that geometric signs serve as markers of a structured ethnic identity, as found with Aurignacian personal ornaments in @Vanhaeren_d. However, the data used by @Vanhaeren_d was also analyzed by @Kovacevic_Shennan_Vanhaeren_dErrico_Thomas_2015 to find that cultural identity by-descent with modification and isolation-by-distance is a more likely explanation for the distribution of Aurignacian personal ornaments. Our results support the pattern of cultural identity by-descent with modification (although they do not support isolation-by-distance [@tbl-mantel-table]), as well as the patterns of signs and other artwork as a form of communication of cultural in-group and out-group boundaries proposed by @Sauvet_2018 and @baker2024evidence.

>>>>

Our results do not suggest that geometric signs serve as markers of a structured ethnic identity, as found with Aurignacian personal ornaments in @Vanhaeren_d. However, the data used by @Vanhaeren_d was also analyzed by @Kovacevic_Shennan_Vanhaeren_dErrico_Thomas_2015 to find that cultural identity by-descent with modification and isolation-by-distance is a more likely explanation for the distribution of Aurignacian personal ornaments. Our results support the pattern of cultural identity by-descent with modification (although they do not support isolation-by-distance [@tbl-mantel-table]), as well as the patterns of signs and other artwork as a form of cultural in-group and out-group communication found by @Sauvet_2018 and
@baker2024evidence.
